FoRTE baseline

### 2019-04-23 analysis/paper/paper.Rmd
Use facets (not colors) for summary plot

```{r summary-captions}
summary_ts_cap <- paste(
  "ED2 plot-level predictions by model configuration."
)

bigfacet_cap <- paste(
  "ED2 PFT-level predictions of leaf area index (LAI) by model configuration and parameterization."
)
```

```{r summary-ts-plot, fig.cap = summary_ts_cap, fig.dim = c(10, 7)}
readd(summary_ts_plot)
```

@@

```{r bigfacet-plot, fig.cap = bigfacet_cap, fig.dim = c(12, 12)}
readd(bigfacet_plot)
```

@@

```{r captions}
lai_10yr_cap <- paste(
  "ED2 leaf area index (LAI) predictions by plant functional type."
)

rad_barplot_cap <- paste(
  "Comparison of radiation profiles under two-stream and multiple scatter",
  "canopy radiative transfer models."
)
```

```{r lai_10yr, fig.cap = lai_10yr_cap, fig.dim = c(10, 7)}
readd(results_plot)
```

`r mdcap(lai_10yr_cap)`

@@

```{r rad_prof, fig.cap = rad_barplot_cap, fig.dim = c(5, 7)}
readd(rad_lineplot)
```

@@

```{r captions_uncertainty}
annual_means_cap <- paste(
  "Total annual gross (GPP) and net (NPP) primary productivity,",
  "and maximum annual leaf area index (LAI)",
  "from ED2 parameter ensemble simulations.",
  "Red lines are mean (solid) and min/max (dashed) values",
  "from Hardiman et al. (2013)."
)

annual_lai_workflows_cap <- paste(
  "Max annual leaf area index predictions by plant functional type",
  "across different parameter combinations.",
  "Facets are arranged in order of increasing mean annual NPP",
  "after 1940."
)
```

@@

```{r annual_means, fig.cap = annual_means_cap, fig.dim = c(5, 7)}
## readd(old_ensemble_plot)
```

`r mdcap(annual_means_cap)`

```{r annual_lai_workflows, fig.cap = annual_lai_workflows_cap, fig.dim = c(10, 8)}
readd(old_lai_plot)
```

`r mdcap(annual_lai_workflows_cap)`

>>>>

```{r summary-ts-plot, fig.cap = summary_ts_cap, fig.dim = c(10, 7)}
summary_ts_cap <- paste(
  "ED2 plot-level ensemble predictions of",
  "gross (GPP) and net (NPP) primary productivity,",
  "total leaf area index (LAI), and aboveground biomass (AGB)",
  "by model configuration.",
  "Red lines are mean (dashed) and min/max (dotted) values",
  "from Hardiman et al. (2013)."
)
readd(summary_ts_plot)
```

@@

```{r bigfacet-plot, fig.cap = bigfacet_cap, fig.dim = c(12, 12)}
bigfacet_cap <- paste(
  "ED2 PFT-level predictions of leaf area index (LAI) by model configuration and parameterization."
)
readd(bigfacet_plot)
```

`r mdcap(bigfacet_cap)`

@@

@@

```{r rad_prof, fig.cap = rad_barplot_cap, fig.dim = c(5, 7)}
rad_barplot_cap <- paste(
  "Comparison of radiation profiles under two-stream and multiple scatter",
  "canopy radiative transfer models."
)
readd(rad_lineplot)
```

@@

@@
